Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-09-24 ICLR25/experiments.tex
update table

\begin{table}[b!]	
	\centering
	\begin{tabular}{|c||c|c|c|c|c|}
		\hline
		\text{Number $K$}  &  \bf Utility& Utility (1 layer)& \text{} \cite{ DivideAndSlide} & \text{Random} &\text{Random (1 layer)}\\ \hline
		\hline
		0  &   1.761  &1.761& 1.761 & 1.761  & 1.761\\ \hline
		5  & \bf 1.532  &1.603& 1.704 &  1.729&  1.729 \\ \hline
		10  & \bf 1.371  & 1.517& 1.651 & 1.696 & 1.701\\ \hline
		15  & \bf 1.247  &1.466&  1.599 &  1.653& 1.671\\ \hline
		20  & \bf 1.145  &1.438& 1.557 & 1.619 & 1.635\\ \hline
		25  & \bf 1.061  &1.427& 1.519 &  1.586 &1.601\\ \hline
		30  & \bf 0.989  &1.425& 1.489 & 1.546 & 1.574\\ \hline
		35  & \bf 0.934  &1.424& 1.465 & 1.502 &1.542\\ \hline
		40  & \bf 0.921 &1.424& 1.447 & 1.469 & 1.512\\ \hline
		116 (max) &  0.895 &1.424& 1.424 (max=$61$) & 0.895 &1.424  \\ \hline
	\end{tabular}
	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the 1st and 2nd layer (our utility function vs \cite{ DivideAndSlide} vs random choice).}
	\label{tab:example1}
	\vspace{-0.6cm}
\end{table}

>>>>

\begin{table}[b!]	
	\centering
	\begin{tabular}{|c||c|c|c|c|c|}
		\hline
			&\multicolumn{3}{c|}{Neurons in Layer 2}&\multicolumn{2}{c|}{Neurons in Layer 1 and 2}\\\cline{2-6}
		\text{Number $K$}  & \text{Random} & \cite{ DivideAndSlide} & \bf Utility& \text{Random} &\bf Utility\\ \hline
		\hline
		0  &   1.761  &1.761& 1.761 & 1.761  & 1.761\\ \hline
		5  & \bf   1.729&1.603& 1.704 &  1.729&  1.532 \\ \hline
		10  & \bf  1.701 & 1.517& 1.651 & 1.696 & 1.371\\ \hline
		15  & \bf  1.671 &1.466&  1.599 &  1.653& 1.247\\ \hline
		20  & \bf  1.635 &1.438& 1.557 & 1.619 & 1.145\\ \hline
		25  & \bf  1.601 &1.427& 1.519 &  1.586 &1.061\\ \hline
		30  & \bf 1.574 &1.425& 1.489 & 1.546 & 0.989 \\ \hline
		35  & \bf  1.542 &1.424& 1.465 & 1.502 &0.934 \\ \hline
		40  & \bf 1.512 &1.424& 1.447 & 1.469 &0.921 \\ \hline
		116 (max) & 1.424  &1.424& 1.424 (max=$61$) & 0.895 &0.895   \\ \hline
	\end{tabular}
	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the 1st and 2nd layer (our utility function vs \cite{ DivideAndSlide} vs random choice).}
	\label{tab:example1}
	\vspace{-0.6cm}
\end{table}
